---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qbr

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/qbr)](https://cran.r-project.org/package=qbr)
[![CRAN RStudio mirror downloads](https://cranlogs.r-pkg.org/badges/qbr)](https://cran.r-project.org/package=qbr)
<!-- badges: end -->

The goal of qbr is to make it easy to interact with Quickbase's JSON API.

## Installation

You can install the development version of qbr like so:

``` r
 library(devtools)
 install_github("BHII-KSC/qbr")
```

## Functions

|API page|Function|Description|
|:---|:---|:---|
|[Users](https://developer.quickbase.com/operation/getUsers)|`get_users`|Returns a tibble with details of each user in an account|
|[User token](https://developer.quickbase.com/operation/cloneUserToken)|`clone_token`|Copy a usertoken|
|[User token](https://developer.quickbase.com/operation/deactivateUserToken)|`deactivate_token`|Deactivate a usertoken|
|[User token](https://developer.quickbase.com/operation/deleteUserToken)|`delete_token`|Delete a usertoken|
|[Apps](https://developer.quickbase.com/operation/getApp)|`get_app`|Get metadata for an app|
|[Apps](https://developer.quickbase.com/operation/copyApp)|`copy_app`|Copy an app|
|[Apps](https://developer.quickbase.com/operation/deleteApp)|`delete_app`|Delete an app|
|[Apps](https://developer.quickbase.com/operation/getAppEvents)|`get_app_events`|Returns a tibble of triggerable events|
|[Tables](https://developer.quickbase.com/operation/getAppTables)|`get_tables`|Get metadata for all tables in an app|
|[Fields](https://developer.quickbase.com/operation/getFields)|`get_fields`|Get metadata for all fields in a table|
|[Fields](https://developer.quickbase.com/operation/deleteFields)|`delete_fields`|Delete one or more fields in a table|
|[Reports](https://developer.quickbase.com/operation/getReport)|`get_report`|Returns a named list of metadata for the specified report|
|[Reports](https://developer.quickbase.com/operation/getTableReports)|`get_reports`|Returns a tibble of metadata for each report in a table|
|[Reports](https://developer.quickbase.com/operation/runReport)|`run_report`|Returns a tibble containing all data in the specified report|
|[Records](https://developer.quickbase.com/operation/deleteRecords)|`delete_records`|Deletes records matching query conditions|
|[Records](https://developer.quickbase.com/operation/upsert)|`update_records`|Inserts and/or updates record(s)|
|[Records](https://developer.quickbase.com/operation/runQuery)|`query_records`|Returns a tibble with data matching query conditions|
|N/A|`summarize_app`|Get metadata for an app and its users, tables, and fields|

## Usage

It is often cumbersome to manually download data from Quickbase to work on it in R.
`run_report` makes it easy to extract report data via the Quickbase JSON API:

```{r}
library(qbr)

# Get data from a Quickbase report as a tibble
run_report(subdomain = "bhi",
       auth = keyring::key_get("qb_example"),
       table_id = "bn9d8iesz",
       report_id = "7")

```

Notice that this function returns a tibble even though the payload from Quickbase
is non-tabular JSON. This function extracts data from the Quickbase report 
(recursively if needed to handle the API's auto-pagination) and then makes the
data tidy using 'tidyverse' principles. 


If you don't know the report ID of the report you want to retrieve data from,
you can use `get_reports` to retrieve metadata about all reports in a table:

```{r}
library(qbr)

get_reports(subdomain = "bhi",
            auth = keyring::key_get("qb_example"),
            table_id = "bn9d8iesz")
```


It's sometimes helpful to manage user tokens programmatically:

```{r}
library(qbr)

# Clone a user token. The 'clone_name' must be unique. 
token <- clone_token(subdomain = "bhi", 
                     auth = keyring::key_get("qb_example"),
                     clone_name = "My new token",
                     clone_desc = "A token cloned by an R script")

# The token passed to 'auth' is deleted. Token supplied must be active.
delete_token(subdomain = "bhi", auth = token)

```


You can manage apps using the app functions:
```{r}
library(qbr)

# Copy an app and print the new app's ID
app <- copy_app(subdomain = "bhi",
                auth = keyring::key_get("qb_example"),
          	    app_id = "bn9d8f78g",
          	    app_name = "R Testing copy",
          	    app_desc = "Used to test copy_app() from qbr package",
          	    keep_data = TRUE)

print(app$id)

# Delete the newly created app
delete_app(subdomain = "bhi",
           auth = keyring::key_get("qb_example"),
           app_id = app$id,
           app_name = app$name)

# Get the triggerable events of an app
get_app_events(subdomain = "bhi",
               auth = keyring::key_get("qb_example"),
               app_id = "bn9d8f78g")

```

## Complex data types

This packages returns some field types slightly differently to a Quickbase report:
```{r echo = FALSE, results ='asis'}
library(tibble)
library(knitr)

kable(tribble(~`Field type`, ~`Returned data type`,
        "Multi-select text", "Semicolon-separated text",
        "User", "User's email address",
        "List-user", "Semicolon-separated email addresses"))
```


## Limitations

Some extended ASCII characters (codes 128-255) cannot be properly parsed when 
converting from JSON at present, such as ’ (&#146). Reports containing text and 
rich-text fields are the most likely to suffer an error resulting from the use of 
these extended characters. 

This package makes no attempt to convert data types. Number fields in Quickbase
may well be interpreted in the resulting tibble as characters. The run_report function
does provide a type_suffix argument to allow you to discern the intended datatype
more easily.

